---
title: "Weight of Fish"
author: "Evelyn Chairez / Summer 2024"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

```{r}
fullup <- lm(Weight~ .,data=Perch)
summary.lm(fullup)
```

### Best Models

The data for the Adjusted Squared has a best model for Length1. We can determine this summary has a p-value of 2.2e-16.

### Best Two regressor model

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="Adjusted R^2")
```
  
Using the above chart, we can see that the best regression models are Height and Weight. This model is the best for the Perch data, as well as for the two element model.

## Pike



### Best Models



### Best Two regressor model



## Roach



### Best Models



### Best Two regressor model



## Final Summary Statements


